MSHS COVID-19 Vaccinations

### 2021-12-10 Combined Dashboard Arrived and Sched Appts.Rmd
Create new script for combined dashboard showing cumulative doses to date and arrived and scheduled appointments from yesterday out two weeks.

# Store today's date
today <- Sys.Date()
yesterday <- today - 1

@@

# Specify Sinai colors for table
sinai_colors <- c("#221f72", "#C4C3EF",
                  "#00AEEF", "#B3EBFF",
                  "#D80B8C", "#FBB6E2")

@@

# Summarize schedule data for Epic sites by key stratification
epic_sched_summary <- epic_sched_to_date %>%
  filter(Status2 %in% c("Arr", "Sch") &
           ApptDate <= today + 7) %>%
  group_by(Site,
           VaxType,
           Dose,
           VaccWeek,
           WeekDates,
           ApptDate,
           Status2) %>%
  summarize(Count = n(),
            .groups = "keep") %>%
  pivot_wider(names_from = Dose,
              names_prefix = "Dose",
              values_from = Count) %>%
  mutate(AllDoses = sum(Dose1, Dose2, Dose3, na.rm = TRUE)) %>%
  pivot_longer(cols = c("Dose1", "Dose2", "Dose3", "AllDoses"),
               names_to = "Dose",
               values_to = "Count") %>%
  mutate(Count = replace_na(Count, 0)) %>%
  filter(!(VaxType %in% c("Peds") & Dose %in% c("Dose3"))) %>%
  ungroup()

@@

    kable(arr_visits_kable_df, format = "html", escape = FALSE,
        align = "c", digits = 0,
        caption = paste0(vax_type, " ", dose_title, ": Administered Doses To Date")) %>%
    kable_styling(bootstrap_options = "hover", position = "center",
                  font_size = 11, full_width = FALSE) %>%
    column_spec(column = c(1,
                           2,
                           ncol(arr_visits_kable_df)),
                border_right = "thin solid lightgray") %>%
    column_spec(column = c(3:ncol(arr_visits_kable_df)),
                background = sinai_colors[2]) %>%
    row_spec(row = nrow(arr_visits_kable_df),
             background = "lightgrey",
             bold = T,
             italic = T,
             color = "black") %>%
    add_header_above(arr_visits_kable_headers,
                     background = c("",
                                    sinai_colors[1]),
                     line = FALSE,
                     color = "white") %>%
    scroll_box(width = "800px")
  }
}
```

```{r Subset data and create custom function for visualizing schedule over next 7 days}

sch_visits <- daily_sched_summary %>%
  filter(Status2 %in% c("Sch")) %>%
  group_by(Site,
           VaxType,
           Dose,
           ApptDate) %>%
  summarize(Count = sum(Count, na.rm = TRUE))

# Create template of today through the next 7 days for each site and dose to ensure holidays are included
today_to_7days <- seq(from = today, to = today + 7, by = 1)

today_to_7days_templ <- data.frame("ApptDate" = rep(today_to_7days,
                                          length(all_sites)))

site_7day_sched_templ <- data.frame("Site" = sort(rep(all_sites,
                                                        length(today_to_7days)
                                                        )
                                                    ),
                                      "ApptDate" = today_to_7days_templ)

site_vax_dose_7day_sched_templ <- left_join(site_vax_dose_templ,
                                            site_7day_sched_templ,
                                            by = c("Site" = "Site"))

sch_visits <- left_join(site_vax_dose_7day_sched_templ,
                          sch_visits,
                          by = c("Site" = "Site",
                                 "VaxType" = "VaxType",
                                 "Dose" = "Dose",
                                 "ApptDate" = "ApptDate"))

sch_visits_kable <- function(vax_type, dose) {
  if (!(vax_type %in% c("Adult", "Peds") |
        dose %in% c(1, 2, 3, "All"))) {
    msg <- "Invalid argument"
    stop(msg)
  } else {

    sch_visits_totals <<- sch_visits %>%
      filter(VaxType %in% vax_type) %>%
      mutate(VaxType = NULL,
             Count = replace_na(Count, 0)) %>%
      arrange(Site, Dose, ApptDate) %>%
      pivot_wider(names_from = c(Dose, ApptDate),
                  names_sep = "__",
                  values_from = Count,
                  names_sort = FALSE) %>%
      adorn_totals(where = "row",
                   na.rm = TRUE,
                   name = "MSHS") %>%
      pivot_longer(cols = contains("__", ignore.case = TRUE),
                   names_to = c("Dose", "Date"),
                   names_sep = "__",
                   values_to = "Count") %>%
      mutate(Date = format(as.Date(Date, "%Y-%m-%d"), "%m/%d")) %>%
      pivot_wider(names_from = c(Site, Dose),
                  names_sep = "__",
                  values_from = Count) %>%
      adorn_totals(where = "row",
                   na.rm = TRUE,
                   name = "Total") %>%
      pivot_longer(cols = contains("__", ignore.case = TRUE),
                   names_to = c("Site", "Dose"),
                   names_sep = "__",
                   values_to = "Count") %>%
      relocate(Site) %>%
      relocate(Dose, .after = Site) %>%
      mutate(Site = factor(Site, levels = c(all_sites, "MSHS"), ordered = TRUE),
             Dose = factor(Dose, levels = doses, ordered = TRUE)) %>%
      arrange(Site, Dose) %>%
      pivot_wider(names_from = Date,
                  values_from = Count)
    dose_filter <- ifelse(dose %in% c(1:3), paste0("Dose", dose),
                          paste0(dose, "Doses"))

    sch_visits_kable_df <<- sch_visits_totals %>%
      filter(Dose == dose_filter) %>%
      mutate(Dose = NULL)

    sch_visits_kable_headers <-
      c(" " = 1,
        "Scheduled Appointments" = ncol(sch_visits_kable_df) - 1)

    kable(sch_visits_kable_df, format = "html", escape = FALSE,
          align = "c", digits = 0,
          caption = paste0(vax_type, " ", dose_title, ": Scheduled Appointments")) %>%
      kable_styling(bootstrap_options = "hover", position = "center",
                    font_size = 11, full_width = FALSE) %>%
      column_spec(column = c(1,
                             ncol(sch_visits_kable_df) - 1,
                             ncol(sch_visits_kable_df)),
                  border_right = "thin solid lightgray") %>%
      row_spec(row = nrow(sch_visits_kable_df),
               background = "lightgrey",
               bold = T,
               italic = T,
               color = "black") %>%
      add_header_above(sch_visits_kable_headers,
                       background = c("",
                                      sinai_colors[1]),
                       line = FALSE,
                       color = "white")
  }
}

@@

sch_visits_kable(vax_type = "Adult", dose = "All")

@@

sch_visits_kable(vax_type = "Adult", dose = 1)

@@

sch_visits_kable(vax_type = "Adult", dose = 2)

@@

sch_visits_kable(vax_type = "Adult", dose = 3)

@@

sch_visits_kable(vax_type = "Peds", dose = "All")

@@

sch_visits_kable(vax_type = "Peds", dose = 1)

@@

sch_visits_kable(vax_type = "Peds", dose = 2)

>>>>

# Store today's date
today <- Sys.Date() - 1
yesterday <- today - 1

@@

# Specify Sinai colors for table
sinai_colors <- c("Dark Blue" = "#221f72",
                  "Light Purple" = "#C4C3EF",
                  "Aqua" = "#00AEEF",
                  "Light Blue" = "#B3EBFF",
                  "Hot Pink" = "#D80B8C",
                  "Light Pink" = "#FBB6E2")

@@

# Summarize schedule data for Epic sites by key stratification
epic_sched_summary <- epic_sched_to_date %>%
  filter(Status2 %in% c("Arr", "Sch") &
           ApptDate <= today + 14) %>%
  group_by(Site,
           VaxType,
           Dose,
           VaccWeek,
           WeekDates,
           ApptDate,
           Status2) %>%
  summarize(Count = n(),
            .groups = "keep") %>%
  pivot_wider(names_from = Dose,
              names_prefix = "Dose",
              values_from = Count) %>%
  mutate(AllDoses = sum(Dose1, Dose2, Dose3, na.rm = TRUE)) %>%
  pivot_longer(cols = c("Dose1", "Dose2", "Dose3", "AllDoses"),
               names_to = "Dose",
               values_to = "Count") %>%
  mutate(Count = replace_na(Count, 0)) %>%
  filter(!(VaxType %in% c("Peds") & Dose %in% c("Dose3"))) %>%
  ungroup()

@@

    kable(arr_visits_kable_df, format = "html", escape = FALSE,
        align = "c", digits = 0,
        caption = paste0(vax_type, " ", dose_title, ": Administered Doses To Date")) %>%
    kable_styling(bootstrap_options = "hover", position = "center",
                  font_size = 11, full_width = FALSE) %>%
    column_spec(column = c(1,
                           2,
                           ncol(arr_visits_kable_df)),
                border_right = "thin solid lightgray") %>%
    # column_spec(column = c(3:ncol(arr_visits_kable_df)),
    #             background = sinai_colors[2]) %>%
    row_spec(row = nrow(arr_visits_kable_df),
             background = "lightgrey",
             bold = T,
             italic = T,
             color = "black") %>%
    add_header_above(arr_visits_kable_headers,
                     background = c("",
                                    sinai_colors["Dark Blue"]),
                     line = FALSE,
                     color = "white") %>%
    scroll_box(width = "800px",
               box_css = "margin: auto;")
  }
}
```

```{r Subset data for appointments arrived yesterday, today, and scheduled for the next 2 weeks}

# Create a template of dates from yesterday out 2 weeks for each site and dose to ensure holidays/weekends are included
# First create a template of yesterday and today's date for appointments that have beena arrived
yest_today <- seq(from = yesterday,
                    to = today, by = 1)

yest_today_status <- data.frame("ApptDate" = yest_today,
                                "Status" = "Arr")

# Then create a template of today out 2 weeks for appointments in scheduled status
today_2wks <- seq(from = today,
                  to = today + 14,
                  by = 1)

today_2wks_status <- data.frame("ApptDate" = today_2wks,
                                "Status" = "Sch")

# Combine the arrived and scheduled appt status data frames
yest_2wks_status <- rbind(yest_today_status,
                          today_2wks_status)

yest_2wks_status <- yest_2wks_status %>%
  arrange(ApptDate, Status)

# Repeate the dates and appt statuses for all sites
yest_2wks_status_site <- bind_rows(
  replicate(length(all_sites),
            yest_2wks_status,
            simplify = FALSE
            )
)

# Create a dataframe of all sites repeated for arrived and scheduled appt status
sites_yest_2wks <- data.frame("Site" = rep(all_sites,
                       nrow(yest_2wks_status)))

sites_yest_2wks <- sites_yest_2wks %>%
  arrange(Site)

# Combine the two templates
yest_2wks_status_site_templ <- cbind(yest_2wks_status_site,
                                     sites_yest_2wks)

# Combine date, appointment status, and site datagrame with vaccine dose and type dataframe
yest_2wks_status_site_vax_dose_templ <- left_join(
  yest_2wks_status_site_templ,
  site_vax_dose_templ,
  by = c("Site" = "Site")
)

# Subset arrived visits yesterday and today and scheduled visits through the next 2 weeks

yest_2wks_arr_sch_visits <- daily_sched_summary %>%
  filter(ApptDate >= yesterday &
           ApptDate <= today + 14) %>%
  group_by(Site,
           VaxType,
           Dose,
           Status2,
           ApptDate) %>%
  summarize(Count = sum(Count, na.rm = TRUE))

# Combine with template to ensure no dates, sites, doses, etc. are missing
yest_2wks_arr_sch_visits <- left_join(
  yest_2wks_status_site_vax_dose_templ,
  yest_2wks_arr_sch_visits,
  by = c("ApptDate" = "ApptDate",
         "Status" = "Status2",
         "Site" = "Site",
         "Dose" = "Dose",
         "VaxType" = "VaxType")
)

arr_sch_visits_kable <- function(vax_type, dose) {
  if (!(vax_type %in% c("Adult", "Peds") |
        dose %in% c(1, 2, 3, "All"))) {
    msg <- "Invalid argument"
    stop(msg)
  } else {

    # Filter for dataframe based on custom function user input
    dose_filter <- ifelse(dose %in% c(1:3), paste0("Dose", dose),
                          paste0(dose, "Doses"))

    # Title for table based on user input
    dose_title <- ifelse(dose %in% c(1:3), paste("Dose", dose),
                         paste (dose, "Doses"))

    # Format dataframe of arrived and scheduled visits for kable visualization
    arr_sch_visits_totals <<- yest_2wks_arr_sch_visits %>%
      # Filter on vaccine type and dose
      filter(VaxType %in% vax_type &
               Dose %in% dose_filter) %>%
      mutate(
        # Remove vaccine type and dose columns
        VaxType = NULL,
        Dose = NULL,
        # Replace any NA with 0 for better visualization
        Count = replace_na(Count, 0)) %>%
      arrange(Site, ApptDate, Status) %>%
      # Pivot wider and calculate totals across health system for each day
      pivot_wider(names_from = c(Status, ApptDate),
                  names_sep = "_",
                  values_from = Count,
                  names_sort = FALSE) %>%
      adorn_totals(where = "row",
                   na.rm = TRUE,
                   name = "MSHS") %>%
      # Pivot longer and reformat date from character to date
      pivot_longer(cols = contains("_", ignore.case = TRUE),
                   names_to = c("Status", "Date"),
                   names_sep = "_",
                   values_to = "Count") %>%
      mutate(Date = format(as.Date(Date, "%Y-%m-%d"), "%m/%d")) %>%
      # Pivot wider and calculate totals for each site from yesterday out 2 weeks
      pivot_wider(names_from = c(Status, Date),
                  names_sep = "_",
                  values_from = "Count") %>%
      adorn_totals(where = "col",
                   na.rm = TRUE,
                   name = "Total") %>%
      # Convert sites to factor for improved visualizations
      mutate(
        Site = factor(Site, levels = c(all_sites, "MSHS"), ordered = TRUE)
      ) %>%
      arrange(Site)

    # Determine kable headers based on dataframe column names
    kable_headers <- c(" " = 1,
                       # Determine columns for arrived visits
                       "Arrived Appts" = max(
                         which(str_detect(colnames(arr_sch_visits_totals),
                                          "Arr")
                         )
                       ) - 
                         min(
                           which(str_detect(colnames(arr_sch_visits_totals),
                                            "Arr")
                           )
                         ) + 1,

                       # Determine columns for scheduled visits
                       "Scheduled Appts" = max(
                         which(str_detect(colnames(arr_sch_visits_totals),
                                          "Sch")
                         )
                       ) -
                         min(
                           which(str_detect(colnames(arr_sch_visits_totals),
                                            "Sch")
                           )
                         ) + 1,
                       # Determine column for total visits
                       "Total" = max(
                         which(str_detect(colnames(arr_sch_visits_totals),
                                          "Total")
                         )
                       ) -
                         min(
                           which(str_detect(colnames(arr_sch_visits_totals),
                                            "Total")
                           )
                         ) + 1
    )

    # Create kable for visualizing appointment volume from yesterday out 2 weeks
    kable(arr_sch_visits_totals,
          format = "html",
          # Update column names to only show dates, where applicable
          col.names = gsub("[A-Za-z]+\\_", "",
                       colnames(arr_sch_visits_totals)),
          escape = FALSE,
          align = "c",
          digits = 0,
          caption = paste0(vax_type,
                           " ",
                           dose_title,
                           ": Arrived & Scheduled Appts")) %>%
      kable_styling(bootstrap_options = "hover",
                    position = "center",
                    font_size = 11,
                    full_width = FALSE) %>%
      column_spec(column = c(1,
                             max(
                               which(
                                 str_detect(colnames(arr_sch_visits_totals),
                                            "Arr")
                               )
                             ),
                             max(
                               which(
                                 str_detect(colnames(arr_sch_visits_totals),
                                            "Sch")
                                 )
                             ),
                             ncol(arr_sch_visits_totals)
                             ),
                  border_right = "thin solid lightgray") %>%
      row_spec(row = nrow(arr_sch_visits_totals),
               background = "lightgrey",
               bold = T,
               italic = T,
               color = "black") %>%
      add_header_above(kable_headers,
                       background = c("",
                                      sinai_colors["Aqua"],
                                      sinai_colors["Dark Blue"],
                                      sinai_colors["Hot Pink"]),
                       line = FALSE,
                       color = "white")
  }
}

@@

arr_sch_visits_kable(vax_type = "Adult", dose = "All")

@@

arr_sch_visits_kable(vax_type = "Adult", dose = 1)

@@

arr_sch_visits_kable(vax_type = "Adult", dose = 2)

@@

arr_sch_visits_kable(vax_type = "Adult", dose = 3)

@@

arr_sch_visits_kable(vax_type = "Peds", dose = "All")

@@

arr_sch_visits_kable(vax_type = "Peds", dose = 1)

@@

arr_sch_visits_kable(vax_type = "Peds", dose = 2)
